My title

### 2024-03-15 paper/paper.qmd
Updated

## 1.2. Data Overview.

@@

Examining the top ten causes in 2021 reveals several notable findings (@fig-dataset-overview). For example, ...

@@

```{r}
#| label: fig-summary_table
#| echo: false
#| fig-cap:   Summary statistics of the number of yearly deaths, by cause, in Alberta, Canada
#| warning: false
#| message: false
summary(alberta_cod$total_deaths)
```

@@

poisson <- loo(cause_of_death_alberta_poisson, cores = 2)
neg_binomial <- loo(cause_of_death_alberta_neg_binomial, cores = 2)

>>>>

@@

Examining the top ten causes in 2022 reveals several notable findings (@fig-dataset-overview). For example, ...

@@

```{r}
#| label: fig-summary_table
#| echo: false
#| fig-cap:   Summary statistics of the number of yearly deaths, by cause, in Alberta, Canada
#| warning: false
#| message: false
# Calculate summary statistics for total_deaths
summary_stats <- data.frame(
  Min = min(alberta_cod$total_deaths, na.rm = TRUE),
  Mean = mean(alberta_cod$total_deaths, na.rm = TRUE),
  Max = max(alberta_cod$total_deaths, na.rm = TRUE),
  SD = sd(alberta_cod$total_deaths, na.rm = TRUE),
  Var = var(alberta_cod$total_deaths, na.rm = TRUE),
  N = sum(!is.na(alberta_cod$total_deaths))
)

# Print the summary statistics
print(summary_stats)

@@

poisson <- loo(cause_of_death_alberta_poisson, cores = 1)
neg_binomial <- loo(cause_of_death_alberta_neg_binomial, cores = 1)
